What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-25 lda-paper.tex
slight edits

  As development on a software project progresses, developers shift their focus between different topics and tasks many
  times.  Managers and newcomer developers often seek ways of
  understanding what tasks have recently been worked on and how much
  effort has gone into each; for example, a manager might wonder what
  unexpected tasks occupied their team's attention during a period
  when they were supposed to have been implementing a set of new
  features.  Tools such as Latent Dirichlet Allocation (LDA) and
  \hla{
    Latent Semantic Indexing (LSI) can be used to analyze commit log
  }
  comments over the entire lifetime of a project. Previous work on
  developer topic analysis has leveraged these tools to associate
  commit log comments with independent topics extracted from these
  commit log comments.  In this paper, we use LDA  to analyze
  periods, such as months, within a project's lifetime to create a
  time-windowed model of changing development topics.  We propose 
  visualizations of this model that allows us to explore the evolving
  stream of topics of development occurring over time.  We demonstrate
  that windowed topic analysis offers advantages over topic analysis
  applied to a project's lifetime because many topics are quite local.

>>>>

  As development on a software project progresses, developers shift
  their focus between different topics and tasks many times. Managers
  and newcomer developers often seek ways of understanding what tasks
  have recently been worked on and how much effort has gone into each;
  for example, a manager might wonder what unexpected tasks occupied
  their team's attention during a period when they were supposed to
  have been implementing a set of new features.  Tools such as Latent
  Dirichlet Allocation (LDA) and Latent Semantic Indexing (LSI) can be
  used to extract a set of independent topics from a corpus of commit
  log comments.  Previous work in the area has created a single set of
  topics by analyzing comments from the entire lifetime of the
  project.  In this paper, we propose windowing the topic analysis to
  give a more nuanced view of the system's evolution. By using a
  defined time-window of, for example, one month, we can track which
  topics come and go over time, and which ones recur. We propose
  visualizations of this model that allows us to explore the evolving
  stream of topics of development occurring over time. We demonstrate
  that windowed topic analysis offers advantages over topic analysis
  applied to a project's lifetime because many topics are quite
  local.

%   As development on a software project progresses, developers shift
%   their focus between different topics and tasks many times.  Managers
%   and newcomer developers often seek ways of understanding what tasks
%   have recently been worked on and how much effort has gone into each;
%   for example, a manager might wonder what unexpected tasks occupied
%   their team's attention during a period when they were supposed to
%   have been implementing a set of new features.  Tools such as Latent
%   Dirichlet Allocation (LDA) and \hla{ Latent Semantic Indexing (LSI)
%     can be used to analyze commit log } comments over the entire
%   lifetime of a project. Previous work on developer topic analysis has
%   leveraged these tools to associate commit log comments with
%   independent topics extracted from these commit log comments.  In
%   this paper, we use LDA to analyze periods, such as months, within a
%   project's lifetime to create a time-windowed model of changing
%   development topics.  We propose visualizations of this model that
%   allows us to explore the evolving stream of topics of development
%   occurring over time.  We demonstrate that windowed topic analysis
%   offers advantages over topic analysis applied to a project's
%   lifetime because many topics are quite local.
